### 2016-10-26 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
Edits

```{r Figure 1}

temp <- subset(dd,Age<15)
reps <- tapply(temp$RTL,temp$BirdID,length)
keep <- names(reps[reps>0])
temp <- subset(temp,BirdID %in% keep)
temp <- subset(temp,!duplicated(paste0(BirdID,Agemonths)))

@@

Fig2B <- ggplot(temp,aes(x = Agemonths,y = RTL,col = Cohort))+
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'))+
  geom_smooth(se = F)+
  annotate('text',x = 0,y = 1.4,label = 'B')

@@

#Run the model
lm2 <- lmer(RTL ~  LogAge + Tarsus + Helper + NonHelper + Sex + BodyMass  +CatchMonth + Insect + Density + (1|LayYear) + (1|BirdID) + (1|PlateID),
            data = temp,
            REML = FALSE)
lm2 <- standardize(lm2)

@@

temp$Age2 <- ifelse(temp$Ageclass == 'A',
                    ifelse(temp$Sex == 'Males',
                           'Adult males',
                           'Adult females'),
                    ifelse(temp$Sex == 'Males',
                           'Juvenule males',
                           'Juvenile females'))

Fig3B <- ggplot(temp,
       aes(x = Agemonths,
           y = RTL,
           col = Sex)) +
  ylab('RTL') + 
  xlab('') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'top') +
  stat_smooth(method = 'lm',formula = y~log(x))
  annotate('text',x = 17,y = 2.1,label = 'B')

Fig3C <- ggplot(temp,
       aes(
           y = RTL,
           x=Insect,
           col = Sex)) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'top') +
  geom_point()+
   stat_smooth(method = 'lm',formula = y~log(x))
  # scale_colour_manual(values = c('grey','darkorange','darkgreen'))+
  # scale_fill_manual(values = c('grey','darkorange','darkgreen'))+
  annotate('text',x = 3,y = 2.1,label = 'C')

pdf('Figures/Figure 3.pdf',
    width = 8,
    height = 8,
    paper = 'a4r')
multiplot(Fig3A,Fig3B,Fig3C,layout = matrix(c(1,1,2,3),nrow = 2,byrow = T))
dev.off()

@@

>>>>

```{r Figure 1}
subset
temp <- subset(dd,Age<15)
reps <- tapply(temp$RTL,temp$BirdID,length)
keep <- names(reps[reps>0])
temp <- subset(temp,BirdID %in% keep)
temp <- subset(temp,!duplicated(paste0(BirdID,Agemonths)))

@@

Fig2B <- ggplot(temp,aes(x = Agemonths,y = RTL,col = Cohort))+
  xlab('Age (months)') +
  geom_point()+
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'))+
  geom_smooth(se = F)+
  annotate('text',x = 0,y = 1.4,label = 'B')

@@

#Run the model
lm2 <- lmer(RTL ~  LogAge + Tarsus + Helper + NonHelper + Sex + BodyMass + Insect + Density + (1|LayYear) + (1|BirdID) + (1|PlateID),
            data = temp,
            REML = FALSE)
lm2 <- standardize(lm2)

@@

  Fig3B <- ggplot(temp,
       aes(x = Agemonths,
           y = RTL,
           col = Sex)) +
  geom_point()+
  ylab('RTL') + 
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
  stat_smooth(method = 'lm',formula = y~log(x))+
  annotate('text',x = 1,y = 2.5,label = 'B')

Fig3C <- ggplot(temp,
       aes(x = Tarsus,
           y = RTL,
           col = Sex)) +
  geom_point()+
  ylab('RTL') + 
  xlab('Tarsus length (mm)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
  stat_smooth(method = 'lm')+
  annotate('text',x = 17,y = 2.5,label = 'C')

Fig3D <- ggplot(temp,
       aes(
           y = RTL,
           x=Insect)) +
    ylab('RTL') + 
  xlab('Insect abundance') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
  geom_boxplot(aes(group = Insect),outlier.shape = NA)+
   stat_smooth(method = 'lm',col = 'darkgrey')+
  annotate('text',x = 2.5,y = 2.5,label = 'D')

Fig3E <- ggplot(temp,
       aes(
           y = RTL,
           x=Density)) +
    ylab('RTL') + 
  xlab('Density') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
  geom_boxplot(aes(group = Insect),outlier.shape = NA)+
   stat_smooth(method = 'lm',col = 'darkgrey')+
  annotate('text',x = 270,y = 2.5,label = 'E')

pdf('Figures/Figure 3.pdf',
    width = 8,
    height = 12,
    paper = 'a4')
multiplot(Fig3A,Fig3B,Fig3C,Fig3D,Fig3E,layout = matrix(c(1,1,2,3,4,5),nrow = 3,byrow = T))
dev.off()

@@

ggplot(dd,aes(col = Whodunnit,y = RTL,x = factor(LayYear)))+
geom_boxplot()
